---
title: "Tutorial"
author: "FM 2019 Team"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


Documentation for creating questions found [here](https://rstudio.github.io/learnr/questions.html)

Cool cool nice these are good questions
http://www.mhhe.com/cgi-bin/netquiz_get.pl?qfooter=/usr/web/home/mhhe/socscience/psychology/dunn/quizzes/test7fq.htm&test=/usr/web/home/mhhe/socscience/psychology/dunn/quizzes/test7q.txt&answers=/usr/web/home/mhhe/socscience/psychology/dunn/quizzes/test7a.txt&email=1


Also good resource: 
http://rstatistics.net/linear-regression-with-r-a-numeric-example/

### Coding in R

## Exercise 1: Plotting

*Here's a few exercises to get you started coding up a linear regression.*

The first thing to do with any data set is plot it to get a feel for how the 
data is distributed. 

Let's store the speed from the cars package (cars$speed) as x and distance as y and plot them. 

```{r scatterplot, exercise = TRUE}
x=...
y=...
plot(...)
```
The graph you produced should show you a correlation of speed and distance datapoints. 

Now we can use the `scatter.smooth()` function to create a scatter plot with an added smoothed line of speed vs. distance in the `cars` dataset:

```{r scatter-plot, exercise=TRUE}
scatter.smooth(...)
```

```{r scatter-plot-hint}
# the main relationship we're going to examine is "Dist ~ Speed"
x=cars$speed
y=cars$dist
scatter.smooth(x, y, main=...)
```



## Exercise 2: Maths

Correlation
```{r correlation, exercise=TRUE}
# use the `cor` function!
```

```{r correlation-hint}
cor(cars$speed, cars$dist)  # calculate correlation between speed and distance 
```

Using `lm()`
```{r lm, exercise=TRUE}
# use lm to do some stuff
```

```{r lm-hint}
cor(cars$speed, cars$dist)  # calculate correlation between speed and distance 
```

Now look at the summary
```{r lm-sum, exercise=TRUE}

```

## Questions

The Basics
```{r x-pred, echo=FALSE}
question("In a simple linear regression, the X is the... ",
  answer("predictor", correct = TRUE),
  answer("dependent variable")
)
```

```{r y-dv, echo=FALSE}
question("In a simple linear regression, the Y is the... ",
  answer("predictor"),
  answer("dependent variable", correct = TRUE)
)
```

```{r xy-cont, echo=FALSE}
question("To calculate a simple linear regression, both X and Y need to be (typically)... ",
  answer("categorical/factor"),
  answer("numeric/continuous", correct = TRUE)
)

```

x and y need to be (typically) numeric/continuous  vs categorical/factor
