---
title: "Tutorial"
author: "FM 2019 Team"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


Documentation for creating questions found [here](https://rstudio.github.io/learnr/questions.html)

Cool cool nice these are good questions
http://www.mhhe.com/cgi-bin/netquiz_get.pl?qfooter=/usr/web/home/mhhe/socscience/psychology/dunn/quizzes/test7fq.htm&test=/usr/web/home/mhhe/socscience/psychology/dunn/quizzes/test7q.txt&answers=/usr/web/home/mhhe/socscience/psychology/dunn/quizzes/test7a.txt&email=1


Also good resource: 
http://rstatistics.net/linear-regression-with-r-a-numeric-example/

### Coding in R

## Exercise 1: Plotting

*Here's a few exercises to get you started coding up a linear regression.*

The first thing to do with any data set is plot it to get a feel for how the 
data is distributed. 

Write R Code to create a scatter plot with a smoothed line of speed vs. distance in the `cars` dataset:

```{r scatter-plot, exercise=TRUE}
scatter.smooth(...)
```

```{r scatter-plot-hint}
# the main relationship we're going to examine is "Dist ~ Speed"
x=cars$speed
y=cars$dist
scatter.smooth(x, y, main=...)
```



## Exercise 2: Maths

Correlation
```{r correlation, exercise=TRUE}
# use the `cor` function!
```

```{r correlation-hint}
cor(cars$speed, cars$dist)  # calculate correlation between speed and distance 
```

Using `lm()`
```{r lm, exercise=TRUE}
# use lm to do some stuff
```

```{r lm-hint}
cor(cars$speed, cars$dist)  # calculate correlation between speed and distance 
```

Now look at the summary
```{r lm-sum, exercise=TRUE}

```

